RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
typo fix

`RNeXML` opens up a rich world of both currently available and rapidly
growing data sets in the NeXML format to the R user and the large ecosystem
of R packages currently available for handling phylogenetic data  
R packages and R users frequently add rich information to the phylogenies
they work with, but need a platform independent data exchange format to
share and archive this. We illustrate how NeXML can
be used to distribute both phylogenies and character trait data used in 
many popular phylogenetic comparative methods tools in R.  
`RNeXML` also provides convenient tools for adding metadata
to NeXML files, including the automated generation of metadata and examples
of how to extend the NeXML standard to represent new data features without
breaking validation or backwards compatability of the file type.

>>>>

`RNeXML` opens up a rich world of both currently available and rapidly
growing data sets in the NeXML format to the R user and the large ecosystem
of R packages currently available for handling phylogenetic data  
R packages and R users frequently add rich information to the phylogenies
they work with, but need a platform independent data exchange format to
share and archive this. We illustrate how NeXML can
be used to distribute both phylogenies and character trait data used in 
many popular phylogenetic comparative methods tools in R.  
`RNeXML` also provides convenient tools for adding metadata
to NeXML files, including the automated generation of metadata and examples
of how to extend the NeXML standard to represent new data features without
breaking validation or backwards compatibility of the file type.
